Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-02 paper.tex
Tunnels

Now that we have a good long-term identity key distribution strategy, we are going to introduce a new transport-layer security protocol that provides safer and faster encrypted connections.
\subsection{MinimaLT}
MinimaLT\cite{MinimaLT} is a protocol that presents some of the interesting features we want. It was initially designed to secure network connections between computers running the secure operating system \emph{Ethos}. In the following sections we are going to see what level of security it provides and why those changes were made. MinimaLT is a newcomer\footnote{Paper published in Mai 2013} that looks really promising.

@@

- Encryption & PFS

@@

- DDoS protection
- IP Mobility

>>>>

Now that we have a good long-term identity key distribution strategy, we are going to introduce a new transport-layer security protocol that provides safer and faster encrypted connections.
\subsection{MinimaLT}
MinimaLT\cite{MinimaLT} is a protocol that presents some of the interesting features we want. It was initially designed to secure network connections between computers running the secure operating system \emph{Ethos}. In the following sections we are going to see what level of security it provides and why those changes were made.\footnote{We are however not going to go over the whole specification of the protocol.} MinimaLT is a newcomer\footnote{Paper published in Mai 2013} that looks really promising.

@@

- Encryption \& PFS

A few months ago, a previously unknown email provider called \emph{Lavabit} got under pressure from the US government to hand over it's private SSL key. The reason turned out to be that Snowden used the email service. If Lavabit turned over the SSL keys, they would compromise the privacy of their entire user base. This is due to poorly configured SSL where the encryption keys used in the handshake are shared between sessions. Unfortunately, most system administrators don't put the \emph{ECDHE} ciphers on top of their ciphers list which results in the lack of Perfect Forward Secrecy.

ECDHE performs a Elliptic curve Diffie–Hellman key exchange. The last E from ECDHE stands for ephemeral, meaning that none of the symmetric keys used for encryption will be stored. Hence, if later the server gets compromised or the network operator is forced to hand over an encryption key this is something that he won't be able to provide.

@@

- IP Mobility

Thanks to the structure of MinimaLT packets, the TunelID is what identifies what packet belongs to what connection and therefore, MinimaLT has complete IP mobility. Unlike TCP, the source IP address and UDP port can change without affecting the connection. A specific RPC (\emph{$\text{nextTid}_{0}$}) exists to announce an IP address change. That call will generate a new tunnel ID and change the keys.

- Handshakes

When establishing a single TLS connection, two hosts have to go through a TCP three-way handshake

- DDoS protection
